Attachment Analysis: Report Project

### 2021-07-02 Documents/Report-Project/Report-analysis.Rmd
revision analysis internalizing

# Cluster
drake::loadd(cluster_mother_tat)
drake::loadd(cluster_father_tat)
drake::loadd(data_cluster_tat)
drake::loadd(mclust_mother)
drake::loadd(mclust_father)

# brms models
drake::loadd(fit_int)
```

@@

# References

>>>>

```

@@

# TODO

## Bayes Factor Encompassing Priors

- [ ] Reparametrize model according to: 
\begin{align}
&\beta_{eq} = R_{eq}\theta - r_{eq},\\
&\beta_{ineq} = R_{ineq}\theta - r_{ineq}.
\end{align}
Doing this we get informative hypotheses as $H_i: \beta_{eq} = 0,\ \beta_{ineeq}>0$, so prior specification is semplified and with simmetric prior we do  not favoir any constraint. Exception for range constraints of type $a<\theta<b$.

- [X] Marginal densities of a multivariate normal distribution are obtained simply dropping irreleevantt variables ([link math-stackexchange](https://math.stackexchange.com/questions/2528201/find-the-marginal-distributions-pdfs-of-a-multivariate-normal-distribution))
# References
